Quantifying maternal reproductive output of chondrichthyan fishes

### 2024-10-25 README.qmd
readme

ggplot()  + 
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  geom_line(data = newdata, aes(x= len, y = matern)) + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition", title = "Length at maternity data for female sandbar sharks")

>>>>

ggplot()  + 
  geom_point(data = data_binned, aes(x = x_bin, y = p), col = "black") + 
  geom_line(data = newdata, aes(x= len, y = matern)) + 
  ylim(0, 1) +
  labs(x = "Fork length (cm)", y = "Proportion in maternal condition", title = "Observed and predicted length at maternity for female sandbar sharks")
